\documentclass{resume}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\usepackage{changepage}   % for the adjustwidth environment
\usepackage{lmodern}

\renewcommand*\familydefault{\sfdefault}
\usepackage[T1]{fontenc}

\name{Harriet Alexander}
\address{ (508)289-3565 | halexander@whoi.edu | AlexanderLabWHOI.github.io}
\address{ 266 Woods Hole Rd. MS\# 51, Woods Hole, MA 02543  }


\usepackage{multibib}
\newcites{ipr,pr}{{ InvitedPresentations},{Presentations}}

\newenvironment{tabbed}{\vspace{-20pt}\begin{adjustwidth}{1cm}{0.2cm}}{\end{adjustwidth}}


\def\nameskip{\bigskip}
\def\sectionskip{\medskip}

% bold name in citations or wherever it appears
 % \def\FormatName#1{%
 %   \def\myname{Alexander H}%
 %   \edef\name{#1}%
 %   \ifx\name\myname
 %     \textbf{#1}%
 %   \else
 %     #1%
 %   \fi
 % }

\usepackage[utf8]{inputenc}


%invert the numbers
\usepackage{etaremune}
\makeatletter
\long\def\thebibliography#1{%
  \section*{\refname}%
  \@mkboth{\MakeUppercase\refname}{\MakeUppercase\refname}
  \settowidth{\dimen0}{\@biblabel{#1}}%
  \setlength{\dimen2}{\dimen0}%
  \addtolength{\dimen2}{\labelsep}
  \sloppy
  \clubpenalty 4000
  \@clubpenalty
  \clubpenalty
  \widowpenalty 4000
  \sfcode `\.\@m 
  \renewcommand{\labelenumi}{\@biblabel{\theenumi}} % labels like [3], [2], [1]
  \begin{etaremune}[labelwidth=\dimen0,leftmargin=\dimen2]\@openbib@code
}
\def\endthebibliography{\end{etaremune}}
\def\@bibitem#1{%
  \item \if@filesw\immediate\write\@auxout{\string\bibcite{#1}{\the\value{enumi}}}\fi\ignorespaces
  }

\makeatother





\begin{document}
\fontfamily{lmss}

  \begin{rSection}{Education}
  
    {\textbf{PhD, Biological Oceanography}, MIT-WHOI Joint Program, Cambridge / Woods Hole, MA} \hfill {\em 2016} \\ 
    { Advisor: Dr. Sonya Dyhrman }  
    
    \smallskip
    
    {\textbf{BA, Biological Sciences}, Wellesley College, Wellesley, MA} \hfill {\em 2010} \\ 
     {Departmental Honors in Biological Sciences, Minor in Mathematics, {\textit{cum laude}}}
    
    
  \end{rSection}

  \begin{rSection}{Professional Experience}
  
    {\textbf{Assistant Scientist}, Biology Department, Woods Hole Oceanographic Institution} \hfill {\em 2018-present}\\
    {Woods Hole, MA}
    
    \smallskip
    
    {\textbf{Postdoctoral Fellow}, University of California, Davis, Davis, CA} \hfill {\em 2016-2018} \\
    {Advisor: Dr. C. Titus Brown}

    \smallskip
    
    {\textbf{Postdoctoral Investigator}, Lamont-Doherty Earth Observatory, Palisades, NY} \hfill {\em 2016} \\
    {Advisor: Dr. Sonya Dyhrman}
    
  \end{rSection}

\begin{rSection}{Selected Awards and Fellowships}
	{Simons Early Career Investigator in Marine Microbial Ecology and Evolution Award} \hfill{\em 2022} \\
	{GigaScience Paper Prize ICG13} \hfill {\em 2018}\\
	{EMBL Travel Award} \hfill {\em 2016}\\
	{NSF ECOGEO Workshop Travel Award} \hfill {\em 2015} \\
	{OCB Trait-based Ecology Conference Travel Award} \hfill {\em 2015}\\
	{Ocean Life Institute Fellowship} \hfill {\em 2014--2015} \\
	{OCB Scoping Workshop Travel Award} \hfill {\em 2014}\\
	{National Defense Science and Engineering Fellowship} \hfill {\em 2011-2014}\\
	{National Science Foundation Graduate Research Fellowship} \hfill \textit{2011 (declined for NDSEG)}\\
	{MIT Presidential Fellowship} \hfill {\em 2010--2011}\\
	{Lucy Allen Branch Prize in Natural History} \hfill {\em 2010}\\
	{Jane Harris Schneider Prize in Sculpture} \hfill {\em 2010}
\end{rSection}

\begin{rSection}{Publications}
	Mentored students and postdocs are \underline{underlined}. * indicates equal contribution and authorship. 
	\renewcommand\refname{}
	\vspace{-36pt}

	\nocite{krinos2023reverse, mars2022microbiomes,Cohen2022,Clayton2022,mcparland2021osmolyte, Krinos2021,mcparland2021dmsp,fiore2021phosphate, Alexander2020, Johnson2020, Choi_2020, Bolyen2019, Wurch2019, Alexander2018, Johnson2018, Hu2018, Rouco2018, Haley2017, Harke2017, Moniruzzaman2017, Kujawinski2017, Guy-Haim2017,Durden2017,Caron2016, Rouco2016,Alexander2015a, Alexander2015,Fischer2014, Alexander2012, Dyhrman2012}

	\bibliographystyle{annoated-cv}
 	% \bibliographystyle{cv}

	\bibliography{publications}

\end{rSection}


\begin{rSection}{Invited Presentations}
	\renewcommand\refnameipr{}
	\vspace{-20pt}
	\nociteipr{*}
	\bibliographystyleipr{annoated-cv}
	\bibliographyipr{invitedpresentations}

\end{rSection}


\begin{rSection}{Selected Abstracts}
	\renewcommand\refnamepr{}
	\vspace{-20pt}
	\nocitepr{*}
	\bibliographystylepr{annoated-cv}
	\bibliographypr{presentations}

\end{rSection}

  \begin{rSection}{Supervision at WHOI}
  
      \begin{rSubsection}{\textit{MIT-WHOI Joint Program Graduate Students}}{}{}{}
          \item  {\textbf{Miah Manning}, June 2023-present.}
          \item  {\textbf{Jo Hickman}, NSF Graduate Fellow, June 2023-present.}
    \item  {\textbf{Arianna Krinos}, co-advised with Mick Follows, Computational Science Graduate Fellowship, June 2019-present.}
        \end{rSubsection}
      \begin{rSubsection}{\textit{WHOI Postdoctoral Scholars}}{}{}{}
    \item  {\textbf{Margaret Mars Brisbin}, November 2020-present, co-advised with Mak Saito, WHOI Postdoctoral Scholar and Simons Foundation Postdoctoral Fellow in Marine Microbial Ecology.}
        \end{rSubsection}
    \begin{rSubsection}{\textit{Other Students}}{}{}{}
    \item  {\textbf{Alese Schofield}, CC-CREW, Summer 2022}
    \item  {\textbf{Patrick White}, Guest Student, MSc Student at University of Alberta, 2021-2023}
    \item  {\textbf{Celeste Nobrega}, Guest Student, Summer 2021}
    \item  {\textbf{Kevin Rice}, Guest Student, Summer 2021}
    \item  {\textbf{Laura Blum}, Summer Student Fellow, Summer 2019}
        \end{rSubsection}
      \begin{rSubsection}{Thesis Committees}{}{}{}
     \item  {\textbf{Serena Sung-Clarke}, MIT Thesis Committee member (MIT-WHOI), 2021-present}
     \item  {\textbf{Max Jahns}, Thesis Committee member, 2021-present}
    \item  {\textbf{David Geller-McGrath}, Thesis Committee member , 2019-present}
    \item  {\textbf{Cynthia Becker}, Thesis Committee member, 2018-2023}
  \end{rSubsection}
      \begin{rSubsection}{\textit{Technical Staff}}{}{}{}
      \item{\textbf{Sara Shapiro}, Research Assistant II, 2021-present}
\end{rSubsection}
    
  \end{rSection}
  
  
\begin{rSection}{Educational Activities}
    
    {\textbf{Instructor}, 12.756 Environmental Bioinformatics, MIT-WHOI Joint Program} \hfill {\em Fall 2019-present} \\
    \begin{tabbed}
         {Co-created and instructed 12-credit graduate course on environmental and non-model bioinformatic approaches with M. Pachiadaki and C. Tepolt. Taught in alternating years.}  
    \end{tabbed}


   {\textbf{Instructor}, MBL Physiology Course, Marine Biological Laboratory} \hfill {\em June 2021} \\
    \begin{tabbed}
         {Organized and taught an introduction to bioinformatics for the MBL Physiology course with a focus on transcriptomics and phylogenetics.}  
    \end{tabbed}

    {\textbf{Instructor}, Software Carpentry, Woods Hole Oceanographic Institution} \hfill {\em June 2021} \\
    \begin{tabbed}
         {Organized and taught Software Carpentry course for WHOI SSFs and incoming JP students, teaching introductory UNIX shell scripting and Python programming.}  
    \end{tabbed}

    {\textbf{Instructor}, Software Carpentry, Woods Hole Oceanographic Institution} \hfill {\em June 2020} \\
    \begin{tabbed}
         {Organized and taught Software Carpentry course for WHOI SSFs and incoming JP students, teaching introductory UNIX shell scripting, Python programming, and Git versioning.}  
    \end{tabbed}

    {\textbf{Lead Instructor}, Environmental Metagenomics Workshop, Data Intensive Biology Summer Institute } \hfill {\em July 2017} \\
    \begin{tabbed}
         {Organized and taught workshop on environmental metagenomic analysis and interpretation.}  
    \end{tabbed}

    {\textbf{Instructor}, Metagenomics Workshop, University of California, Santa Cruz } \hfill {\em April 2017} \\
    \begin{tabbed}
         {Taught workshop on environmental metagenomic analysis and interpretation.}  
    \end{tabbed}

    {\textbf{Instructor}, Metagenomics Workshop, Scripps Institute of Oceanography} \hfill {\em September 2016} \\
    \begin{tabbed}
         {Taught workshop on environmental metagenomic analysis and interpretation.}  
    \end{tabbed}
  {\textbf{Instructor}, Software Carpentry, Woods Hole Oceanographic Institution} \hfill {\em September 2015} \\
    \begin{tabbed}
         {Organized and taught Software Carpentry course at WHOI, teaching introductory UNIX shell scripting, Python programming, and Git versioning.}  
    \end{tabbed}

  {\textbf{Teaching Assistant}, Biological Oceanography, MIT-WHOI Joint Program} \hfill {\em Spring 2014} \\
    \begin{tabbed}
         {Conducted recitation sections, wrote and graded tests, problem sets, and daily assignments, advised professors on student performance.}  
    \end{tabbed}
    
  {\textbf{Writing Tutor}, Pforzheimer Learning and Teaching Center, Wellesley College} \hfill {\em 2007-2010} \\
    \begin{tabbed}
         {Peer tutor trained to assist in all aspects of the writing process-- specialized in writing for the sciences and social sciences.}  
    \end{tabbed}
 {\textbf{Math Tutor and Grader}, Mathematics Department, Wellesley College} \hfill {\em 2009-2010} \\
    \begin{tabbed}
         {Grader for multivariable calculus and number theory. Tutor and assistant for number theory.}  
    \end{tabbed}
\end{rSection}

\begin{rSection}{Professional Activities}
\\

\textbf{\textit{Woods Hole Oceanographic Institution}}

{\textbf{Co-Chair}, HPC Committee} \hfill {\em 2019-present} \\
{\textbf{Member}, SciSec} \hfill {\em 2019-2022} \\
{\textbf{Member}, Biology Chair Search Committee} \hfill {\em 2019} \\ 
{\textbf{Member}, HPC Committee} \hfill {\em 2018-present} 

\textbf{\textit{Outside WHOI}}

\textbf{Member, BCO-DMO Strategic Planning Committee} \hfill {\em 2019-present}\\
\textbf{Session Convener, ASLO Meeting}, Co-chair of session titled “Molecular Insights into \hfill {\em 2017} \\ Adaptive Microbial Physiology” at
ASLO Meeting, Honolulu, HI.\\
\textbf{Session Convener, SciPy}, Co-chair of mini-symposium on "Computational Reproducibility" \hfill {\em 2016} \\  at
SciPy, Austin, TX.

\textbf{\textit{Professional Development and Workshop Participation}}

  {\textbf{Participant}, UNOLS Chief Scientist Training Cruise, Honolulu HI.} \hfill {\em 2019} \\
  {\textbf{Invited Participant}, BioGeoScapes Scoping Workshop, Woods Hole, MA.} \hfill {\em 2018} \\
  {\textbf{Participant}, National Academies Keck Futures Initiative (NAKFI): Discovering the \hfill {\em Fall 2018}
    \\  Deep Blue Sea, Irvine, CA.}  \\
  {\textbf{Participant}, EcoDAS XII: Ecological Dissertations in the Aquatic Sciences, Honolulu, HI.} \hfill {\em 2016} \\
  {\textbf{Invited Participant}, Plant Science Research Network Scenario Modeling \\ Workshop, Chevy Chase, MD.} \hfill {\em 2016} \\
  {\textbf{Participant}, OCB Scoping Workshop: Trait-based approaches to ocean life, Waterville Valley, NH.} \hfill {\em 2015} \\
  {\textbf{Participant}, OCB Scoping Workshop: Improving predictive biogeochemical models \\ through single cell-based analyses of marine plankton, Boothbay, ME.} \hfill {\em 2014} 
  
\textbf{\textit{Reviewer}}
National Science Foundation, NSF Graduate Research Fellowship Program, National Defense Science and Engineering Graduate Fellowshp Program, Moore Foundation, Nature Communications, ISME Journal, Environmental Microbiology, Limnology and Oceanography, Journal of
Phycology, GigaScience



\end{rSection}

\begin{rSection}{Research Cruises}
  {\textbf{UNOLS Chief Scientist Training Cruise; KN19-10}, \textit{R/V Kilo Moana}} \hfill {\em 14-23 June 2019} 


  {\textbf{Seasonal Trophic Roles of \textit{Euphasia suberba} (STRES); NBP14-10}, \textit{R/V Palmer}} \hfill {\em December 2014} \\
    \begin{tabbed}
         {Chief Scientist: Edward Durbin}  
    \end{tabbed}

{\textbf{Deep Dissolved Organic Matter (DeepDOM); KN210-04}, \textit{R/V Knorr}} \hfill {\em March-May 2013} \\
    \begin{tabbed}
         {Chief Scientists: Elizabeth Kujawinski & Krista Longnecker}  
    \end{tabbed}

{\textbf{Hawaii Ocean Experiment (HOE-DYLAN 9); KM12-19}, \textit{R/V Kilo Moana}} \hfill {\em August-September 2012} \\
    \begin{tabbed}
         {Chief Scientist: Sam Wilson}  
    \end{tabbed}

    {\textbf{Hawaii Ocean Experiment (HOE-DYLAN 7); KM12-17}, \textit{R/V Kilo Moana}} \hfill {\em August 2012} \\
    \begin{tabbed}
         {Chief Scientist: Sonya Dyhrman}  
    \end{tabbed}
    
\end{rSection}

\begin{rSection}{Outreach}

  {\textbf{Skype a scientist}, Skyped directly with various elementary - high school classrooms\hfill {\em 2018-present} \\  to share about research and ocean science.} \\
  {\textbf{Submerge!}, New York City marine science festival. Designed and manned booth of hands-on\hfill {\em 2014}\\
activities focused on the biological pump (>4000 in attendance). \\
  {\textbf{Women in Ocean Engineering}, Volunteered weekends to work with middle school age girls \hfill {\em 2014}\\
introducing them to engineering concepts in a marine environment. \\
    {\textbf{Artistic Oceanographer Program}, Combining science and art to teach science concepts. \hfill {\em 2011-2014}\\
    {\textbf{Falmouth Public School Science Fair}, Judged middle and high school science fair. \hfill {\em 2011-2013}\\
    {\textbf{STEM for Girls at the New England Aquarium}, Mentored and volunteered for a \hfill {\em 2012}\\ program to encourage girls to pursue math and science. \\
\end{rSection}

\begin{rSection}{Skills and Certifications}
\textbf{Certifications} Software Carpentry Instructor Training, PADI SCUBA Open Water\\
\textbf{Computation} Python (language of choice), Matlab, R, shell script\\
\textbf{Languages} English, French (conversational)
\end{rSection}


\end{document}

